---
title: Relationship between baseball sporting events and crime activity in southern Chicago
author:
  - name: Parker Franzen
  
  - name: Renhao Sun
   
  - name: Luis Treviño
   
   
affiliation:
  - num: 1
    address: Department of Management Science and Statistics, University of Texas, San Antonio
  - num: 2
    address: Statistical Learning, Dr. Keying Ye
column_numbers: 3

output: 
  posterdown::posterdown_html:
    self_contained: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

The city of Chicago keeps an extensive public record of all reported incidents of crime from 2001 to the present,$^2$  updated every seven days.At the time of analysis for this project this data set contained a total of approximately 7.42 million rows (each row is an incident of a reported crime) and 22 columns. The main interest of this project was to analyze this crime data set along with the incidence of baseball sporting events in the corresponding community areas of Chicago in an effort to see whether a relationship existed among the variables. We specifically looked at the major league baseball team the Chicago White Sox by using their public records of baseball home games from 2001 to the present.$^1$ The Chicago White Sox stadium is located in Guaranteed Rate Field, which is right on the dividing line of community areas 34 (Armour Square) and 60 (Bridgeport). This project focused on the crimes that occurred in these community areas in particular in an effort to see whether or not “game days” (that is, days where there was a formal baseball game in the stadium with a live attendance) had a significant impact on the frequency of reported incidents of crime in those areas. R was used for data manipulation, including removing unnecessary rows and variables, creating new variables to use as predictors in the analysis, merging data on crimes and games into one data set, and more. Web scrapping techniques with R were used in acquiring the data on the dates and times of Chicago White Sox home games.


# Data Structure

This package uses the same workflow approach as the R Markdown you know and love. Basically it goes from RMarkdown > Knitr > Markdown > Pandoc > HTML/CSS > PDF. You can even use the bibliography the same way [@R-posterdown].

# Methods

We first imported the Chicago crimes data set into R and began the data manipulation. Since the baseball stadium is directly in the line of community areas 34 and 60 we grouped these areas together and coded them with a value of “1 - inside area.“ We also identified surrounding Chicago community areas (28, 31, 33, 35, 37, 38, 59, and 61) not directly associated with the stadium and coded them as “0 - outside area.” We proceeded to get rid of all observations that were not associated with these 10 community areas. We also did not include over half of the variables in the original data set because they had no impact or relation to our specific topic of interest (e.g. Case.Number, IUCR, FBI.Code, etc., ). It was then necessary to create a sorted “Date-Time” variable in the format "%Y-%m-%d %H:%M:%S". This was needed for several important reasons. First, for creating and coding a new day/night variable to use in the final model. Next, for aggregating the frequency of crime incident reports according to date (this is the response variable in the final model). Finally, for joining the crimes data set with the games data set into one final data frame in R, containing all the data of interest for this project.  Other variables that were created included; “Game.Day” -- which was coded “1-date is a game day” and “0-date is not a game day; “Weekday”-- which was coded “1-date is on days Monday-Friday” and “0-date is on a weekend day Saturday or Sunday”; and “DayNight” -- which was coded “1-event occurred in the day time” and “0-event occurred in the night time.” Finally, we had a completed data set with a variety of potentially influential variables and were able to run a regression analysis to explore these different factors and to analyze their impact on crime reports in the areas associated with the Chicago White Sox baseball stadium. 

•	Games data set web scraping






```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Results

Aliquam sed faucibus risus, quis efficitur erat. Vestibulum semper mauris quis tempus eleifend. Aliquam sagittis dictum ipsum, quis viverra ligula eleifend ut. Curabitur sagittis vitae arcu eget faucibus. In non elementum felis. Duis et aliquam nunc. Nunc pulvinar sapien nunc, vel pretium nisi efficitur in. Fusce fringilla maximus leo et maximus. Fusce at ligula laoreet, iaculis mi at, auctor odio. Praesent sed elementum justo. Aenean consectetur risus rhoncus tincidunt efficitur. Praesent dictum mauris at diam maximus maximus [@R-posterdown].

# Conclusion

Try `posterdown` out! Hopefully you like it!

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References

1. Baseball Reference. "Chicago White Sox Team History & Encyclopedia". (2021, September 27). Retrieved from https://www.baseball-reference.com/teams/CHW/

2. City of Chicago. "Crimes - 2001 to Present". (2021, October 13). Retrieved from https://data.cityofchicago.org/Public-Safety/Crimes-2001-to-Present/ijzp-q8t2



